Hydra battles in Coq

### 2020-10-21 doc/hydras.tex
initialization of a documentation on Gamma0; strongly critical ordinals

\begin{figure}[h]
  \centering
  \includegraphics[width=11cm]{epsilon0.jpg}
  \caption{Discrete mathematics and formal proofs}
  \label{fig:gamma0}
\end{figure}
 We also hope to provide a little clarification on infinity (both potential and actual) through the notions of function, computation, limit,
 types and proofs.

@@

>>>>

 We also hope to provide a little clarification on infinity (both potential and actual) through the notions of function, computation, limit,
 types and proofs.

@@

\chapter{The ordinal \texorpdfstring{$\Gamma_0$}{Gamma0}}

\textbf{To write!}

\begin{figure}[h]
  \centering
  \includegraphics[width=11cm]{epsilon0.jpg}
  \caption{Discrete mathematics and formal proofs}
  \label{fig:gamma0}
\end{figure}
